### 2016-03-15 paper/icfp16-submission/semantics.tex
remove type contexts

  % By Lemma~\ref{lem:fixme} we know that
  % $\vcompat{\resolve{\vhole{\thole}}{\vsu}}{\resolve{\thole}{\tsu}}$.
  %
  By Lemma~\ref{lem:vsu-ext} we know that
  $\tsu_{i} = \tsu_{i-1}[\thole_1 \mapsto t_1] \ldots [\thole_n \mapsto t_n]$.
  %
  We will assume, without loss of generality, that
  $\tsu_{i} = \tsu_{i-1}[\thole' \mapsto t']$.
  %
  Since $\tsu_{i-1}$ and $\tsu_{i}$ differ only in $\thole'$ but the resolved
  types differ,
  $\ptype{\trace_{i-1}}{f} = \intctx{\thole'}$
  and
  $\ptype{\trace_i}{f} = \intctx{t'}$.
  % $\resolve{\thole}{\tsu_{i-1}} = \intctx{\thole'}$
  % and
  % $\resolve{\thole}{\tsu_{i}} = \intctx{t'}$.
  %
  By Lemma~\ref{lem:context-compat},
  let $s$ be a concrete type such that $\intctx{s} = t$.
  %
  We show by case analysis on the evaluation rules that
  %
  $$\step{e_{i-1}}{\vsu_{i-1}}{\tsu_{i-1}[\thole' \mapsto s]}{\stuck}{\vsu}{\tsu}$$

  Finally, by Lemma~\ref{lem:resolve-compat} we know that
  % $\vsub{\resolve{\thole}{\tsu_{i-1}}}{\resolve{\ehole}{\vsu_{i-1}}}$,
  $\vsub{\ptype{\trace_{i-1}}{f}}{\resolve{\vhole{\thole}}{\vsu_{i-1}}}$
  and thus $\vsub{\intctx{\thole'}}{\resolve{\vhole{\thole}}{\vsu_{i-1}}}$.
  %
  Let
  $$
  \begin{array}{lcl}
  u &=& \gen{s}{\tsu} \\
  v &=& \resolve{\vhole{\thole}}{\vsu_{i-1}}\sub{\ehole'[\thole']}{u}\sub{\thole'}{s} \\
  \end{array}
  $$
  $\steps{\eapp{f}{v}}{\emptysu}{\emptysu}{\stuck}{\vsu}{\tsu}$ in $i$ steps.
  %and
  % $\vsub{\resolve{\thole}{\tsu_{i}}}{\resolve{\ehole}{\vsu_{i}}}$.
  % \vcompat{\resolve{\vhole{\thole}}{\vsu_{i-1}}}{\resolve{\thole}{\tsu_{i-1}}}
  % =
  % \tcompat{\ptype{i-1}{f}}{t}
  % \\
  % \vcompat{\resolve{\vhole{\thole}}{\vsu_{i}}}{\resolve{\thole}{\tsu_{i}}}
  % =
  % \tincompat{\ptype{i}{f}}{t}
  %
  % Finally, by the definition of $\typeofsym$,
  % we know that $\resolve{\vhole{\thole}}{\vsu_{i-1}} = \invctx{v}$
  % such that $\vsub{T'[\thole']}{v}$.
  %such that $\resolve{\typeof{v}}{\tsu_{i-1}} = T'[\thole']$
  %
  %\ES{need to connect \ptype{\trace{i}}{f} and \resolve{\vhole{\thole}}{\vsu_i}}
  %
  % Now, consider any value $u$ such that $\vcompat{\invctx{u}}{t}$,
  % we show by case analysis on the evaluation relation that
  % $\invctx{u}$ could not make progress at this step, and thus
  % $\steps{\eapp{f}{\invctx{u}}}{\emptysu}{\emptysu}{\stuck}{\vsu'}{\tsu'}$.
\end{proof}

>>>>

  % By Lemma~\ref{lem:fixme} we know that
  % $\vcompat{\resolve{\vhole{\thole}}{\vsu}}{\resolve{\thole}{\tsu}}$.
  %
  By Lemma~\ref{lem:vsu-ext} we know that
  $\tsu_{i} = \tsu_{i-1}[\thole_1 \mapsto t_1] \ldots [\thole_n \mapsto t_n]$.
  %
  We will assume, without loss of generality, that
  $\tsu_{i} = \tsu_{i-1}[\thole' \mapsto t']$.
  %
  Since $\tsu_{i-1}$ and $\tsu_{i}$ differ only in $\thole'$ but the resolved
  types differ, we have
  $\thole' \in \ptype{\trace_{i-1}}{f}$
  and
  $\ptype{\trace_i}{f} = \ptype{\trace_{i-1}}{f}\sub{\thole'}{t'}$.
  %
  % We prove\includeTechReport{, in Lemma~\ref{lem:context-compat},}
  % that for all types $s$ and $t$, if.
  Let $s$ be a
  concrete type such that $\ptype{\trace_{i-1}}{f}\sub{\thole'}{s} = t$.
  %
  We show by case analysis on the evaluation rules that
  %
  $$\step{e_{i-1}}{\vsu_{i-1}}{\tsu_{i-1}[\thole' \mapsto s]}{\stuck}{\vsu}{\tsu}$$

  Finally, by Lemma~\ref{lem:resolve-compat} we know that
  % $\vsub{\resolve{\thole}{\tsu_{i-1}}}{\resolve{\ehole}{\vsu_{i-1}}}$,
  $\vsub{\ptype{\trace_{i-1}}{f}}{\resolve{\vhole{\thole}}{\vsu_{i-1}}}$
  and thus $\thole' \in \resolve{\vhole{\thole}}{\vsu_{i-1}}$.
  %and thus $\vsub{\intctx{\thole'}}{\resolve{\vhole{\thole}}{\vsu_{i-1}}}$.
  %
  Let
  $$
  \begin{array}{lcl}
  u &=& \gen{s}{\tsu} \\
  v &=& \resolve{\vhole{\thole}}{\vsu_{i-1}}\sub{\ehole'[\thole']}{u}\sub{\thole'}{s} \\
  \end{array}
  $$
  $\steps{\eapp{f}{v}}{\emptysu}{\emptysu}{\stuck}{\vsu}{\tsu}$ in $i$ steps.
  %and
  % $\vsub{\resolve{\thole}{\tsu_{i}}}{\resolve{\ehole}{\vsu_{i}}}$.
  % \vcompat{\resolve{\vhole{\thole}}{\vsu_{i-1}}}{\resolve{\thole}{\tsu_{i-1}}}
  % =
  % \tcompat{\ptype{i-1}{f}}{t}
  % \\
  % \vcompat{\resolve{\vhole{\thole}}{\vsu_{i}}}{\resolve{\thole}{\tsu_{i}}}
  % =
  % \tincompat{\ptype{i}{f}}{t}
  %
  % Finally, by the definition of $\typeofsym$,
  % we know that $\resolve{\vhole{\thole}}{\vsu_{i-1}} = \invctx{v}$
  % such that $\vsub{T'[\thole']}{v}$.
  %such that $\resolve{\typeof{v}}{\tsu_{i-1}} = T'[\thole']$
  %
  %\ES{need to connect \ptype{\trace{i}}{f} and \resolve{\vhole{\thole}}{\vsu_i}}
  %
  % Now, consider any value $u$ such that $\vcompat{\invctx{u}}{t}$,
  % we show by case analysis on the evaluation relation that
  % $\invctx{u}$ could not make progress at this step, and thus
  % $\steps{\eapp{f}{\invctx{u}}}{\emptysu}{\emptysu}{\stuck}{\vsu'}{\tsu'}$.
\end{proof}
